Active Learning : From Blackbox To Timed Connectors

### 2015-12-25 paper/paper.tex
paper update
.

% used for flow charts
\usepackage{tikz}
% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}
% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows, positioning}

@@

The application of machine learning in formal models has a long history. There are several main
orientations: extraction of formal models and learning-guided verification technique.

@@

@@

\todo{an example as graph}
\begin{figure}[h]
\caption{Infinite States in a Reo Model}
\label{fig:reoinfinite}
\end{figure}

@@

\section{From Blackbox to Timed Connectors}
\subsection{Equivalence Query}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
 no approximation.
\section{Case Studies}

>>>>

% used for flow charts
\usepackage{pgf}
\usepackage{tikz}
\usepackage{reotex}

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}
% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

% declaration of environments
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

@@

To solve this problem, many techniques in model constructing were proposed, for instance in
\cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.

@@

\begin{figure}[h]
  \begin{center}
    \input{./images/basic.tex}
  \end{center}
  \caption{Basic Reo Channels}
  \label{fig:basic}
\end{figure}

@@

\todo{an example as graph}

\subsection{Parameterized Mealy Machine}
\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle S(\Sigma), s_0,
  \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an alphabet to its corresponding Mealy Machine.
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} input/output alphabet
    \item[-] $S$ is a function that maps a \emph{finite} alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ 
  \end{itemize}
\end{definition}

\begin{figure}[h]
\caption{Infinite States in a Reo Model}
\label{fig:reoinfinite}
\end{figure}

@@

\section{From Blackbox to Timed Connectors}
\subsection{Equivalence Query}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
no approximation.

Equivalence queries are used to search for counter-examples. But what makes counter-examples even
existing? In Reo models, we believe that \emph{FIFO} channels and \emph{Timer} channels are to
blame. Here we present a brief example. To make things eaiser, we have only untimed Reo here.

\begin{figure}[h]
  \begin{center}
    \input{./images/3buf.tex}
  \end{center}
  \caption{A Switching Connector $S$ with Three Buffers}
  \label{fig:buf3}
\end{figure}

A \emph{Switching} connector in \figurename \ref{fig:buf3} has two source-ends $A,B$ and one
sink-end $C$. In a nutshell, datum come from $A$ and be stored temporarily in buffers. These datum
will never flow out until signals come to $B$. With the Mealy-Machine semantics given, the semantics
of \emph{Switching} connectors can be defined as following \figurename \ref{fig:buf3semantics}.

\begin{figure}[h]
  \begin{center}
    \input{./images/3bufsemantics.tex}
  \end{center}
  \caption{\emph{Gate} as Mealy Machine $\mathcal{M}(S)$}
  \label{fig:buf3semantics}
\end{figure}

According to the production of Mealy-Machines, 8 different states should be found in
$\mathcal{M}(S)$. We use $q_{abc}$ to denote them. $q_{001}$ indicates that the last buffer is
filled and others are empty, and $q_{111}$ means that there are no space in any buffer. It's
obvious that some states like $q_{100}$ is unreachable.

\begin{definition}[Similar]
  In a mealy machine, two states are similar iff. they have the same output signature.
\end{definition}

\begin{theorem}[Bound of Counter-Example]
  \label{the:cebound} Assume that an observation table has already been closed with maximum
  query length \todo{find a better phrase?} $l$. An counter-example of length $l+2$ would be
  found iff. there're possible counter-examples.
\end{theorem}
\begin{IEEEproof}
  Sketch of this proof are shown in several points:
  \begin{enumerate}
    \item Hypothesises are subgraphs of the semantics graph.
    \item Inputs on reverse edges are complementary.
    \item 
  \end{enumerate}
\end{IEEEproof}

\section{Case Studies}
